A Hitchhiker's Guide to Reproducible Research in R

### 2021-06-24 manuscript.Rmd
restructure the two aims of the paper

This paper has two aims.
First, we want to introduce the reader to a workflow that ensures reproducibility [see @Peikert2019 for details]. 
<!--Second? This is really a different point than introducing the workflow-->We present four common threats to reproducibility and explain how we can address these with a combination of four solutions from the software engineering community.
<!-- Third? -->Specifically, we demonstrate how the R package `repro` supports researchers in implementing this solution.
<!-- Not sure if this belongs in the present paper. If it does, then I wouldn't introduce it as a separate goal. Instead, I would say something like: The present paper introduces the reader to a workflow that ensures reproducibility by building on several technical solutions originating in the software engineering community. We show how these solutions address several common threats to reproducibility, and enable novel solutions further enhancing the open science workflow, such as 'preregistration as code'.  -->The second objective is to present an alternative preregistration scheme that builds upon a reproducible workflow, the so-called preregistration as code (PAC), where the researchers write the complete analysis as code and the bulk of the manuscript, including the sections Introduction, Methods, and Results---initially based on simulated data, before they gather data.
This tutorial is aimed at researchers who intend to ensure the reproducibility of a research project, and are willing to make relevant code, data, and materials available; whether publicly or on request.

@@

While the willingness to share materials is required for reproducing a project, it is not sufficient.<!-- This sounds like the start of a new paragraph-->
For example, @hardwicke2018 attempted to reproduce results from open materials in the journal Cognition. 
Out of 35 published articles, results of 22 articles could be reproduced but in 11 of these cases, assistance from the original authors was required.
For 13 articles, at least one outcome could not be reproduced—--even with the original authors' assistance.
@obels2020 showed that in 62 Registered Reports, 41 had data available, and 37 had analysis scripts available.
The authors could execute only 31 of the scripts without error and reproduce the results of only 21 articles (within a reasonable time).
These failed attempts to reproduce highlight the need for widely accepted reproducibility standards.
The results further illustrate that open repositories do not routinely provide sufficient information to reproduce relevant computational and statistical results.

@@

After introducing the conceptual building blocks, this tutorial guides the reader through each step of an open research project, <!--What does this mean? Isn't the whole paper about reproducibility?-->emphasising guaranteeing reproducibility from the very first step on.
We have structured the tutorial with a _learning by doing_ approach in mind, such that readers can follow along at their own computers.
We explicitly encourage readers to try out all R commands for themselves.
Unless stated otherwise, all code blocks are meant to be run in the statistical programming language R (tested with version `r with(R.version, paste0(major, ".", minor))`).
To guide the reader through all steps of a research project, we will use an exemplary research question:

>>>>

This tutorial is aimed at researchers who intend to ensure the reproducibility of a research project and are willing to make relevant code, data, and materials available, whether publicly or on request.
We pursue two aims.
First, the present paper introduces the reader to a workflow that ensures reproducibility by building on several technical solutions originating in the software engineering community that eliminate four common threats to reproducibility [see @Peikert2019 for details].
Specifically, we demonstrate how the R package `repro` supports researchers in implementing these solutions.
The second objective is to discuss opportunities of such workflow to improve not only how research outputs are created and recreated but also how research itself is conducted.
One such opportunity is an alternative preregistration scheme that builds upon a reproducible workflow, the so-called preregistration as code (PAC), where the researchers write the complete analysis as code and the bulk of the manuscript as dynamic document, including the sections Introduction, Methods, and Results---initially based on simulated data, before they gather data.
This dynamic document which closely resembles an actual journal article but with "fake" results and without discussion of results, then serves as preregistration.

@@

While the willingness to share materials is required for reproducing a project, it is not sufficient.
For example, @hardwicke2018 attempted to reproduce results from open materials in the journal Cognition. 
Out of 35 published articles, results of 22 articles could be reproduced but in 11 of these cases, assistance from the original authors was required.
For 13 articles, at least one outcome could not be reproduced—--even with the original authors' assistance.
@obels2020 showed that in 62 Registered Reports, 41 had data available, and 37 had analysis scripts available.
The authors could execute only 31 of the scripts without error and reproduce the results of only 21 articles (within a reasonable time).
These failed attempts to reproduce highlight the need for widely accepted reproducibility standards.
The results further illustrate that open repositories do not routinely provide sufficient information to reproduce relevant computational and statistical results.

@@

We have structured the tutorial with a _learning by doing_ approach in mind, such that readers can follow along at their own computers.
We explicitly encourage readers to try out all R commands for themselves.
Unless stated otherwise, all code blocks are meant to be run in the statistical programming language R (tested with version `r with(R.version, paste0(major, ".", minor))`).
To guide the reader through all steps of a research project, we will use an exemplary research question:
